%!TEX TS-program = lualatex
\documentclass{nsfbiosketch}
\usepackage{xspace}

\usepackage[resetlabels]{multibib}

%\usepackage{lineno}
%\linenumbers

%shortcuts
\newcommand{\Facet}{\texttt{Facet}\xspace}
\newcommand{\Opal}{\texttt{Opal}\xspace}
\newcommand{\kmer}{$k$-mer\xspace}
\newcommand{\kmers}{$k$-mers\xspace}
\newcommand{\etal}{\xspace\textit{et al.}\xspace}
%------------------------------------------------------------------------------

\name{DeBlasio, Daniel Frank}
\eracommons{danfdeblasio}
\position{Assistant Professor, University of Texas at El Paso}
\nsfid{000808206@nsf.gov} 
\orcid{000-0003-4110-4431}


\newcites{r,o}{Products Most Closely Related to the Proposed Project,Other Significant Products{,} Whether or Not Related to the Proposed Project}



\begin{document}
%------------------------------------------------------------------------------

\textbf{(a) PROFESSIONAL PREPARATION}\\[5pt]
\begin{education}
University of Central Florida & Orlando, FL  & Computer Science & BS           & 2007   \\
University of Central Florida & Orlando, FL & Computer Science & MS           & 2009 \\
University of Arizona & Tucson, AZ               & Computer Science & Ph.D.         & 2006  \\
Carnegie Mellon University & Pittsburgh, PA   & Lane Fellowship, Computational Biology Department & Fellow  & 2016-2019\\
\end{education}
\vspace{10px}\\
\textbf{(b) APPOINTMENTS}\\
\begin{datetbl}
2019 - present	   & Assistant Professor, University of Texas at El Paso, Department of Computer Science, El Paso, TX\\
2016--2019 	& Lane Fellow, Carnegie Mellon University, Computational Biology Department, Pittsburgh, PA\\
2014 - 2016 	& Graduate Research Assistant, University of Arizona, Department of Computer Science, Tucson, AZ\\
2010 - 2014 	& Fellow, University of Arizona, NSF IGERT in Genomics, Tucson, AZ\\
%2010	           	& Research Associate II, Sanford-Burnham Institute for Biomedical Research, Orlando, FL\\
2007 - 2010 	& Developer, University of Central Florida, Engineering Technology Department, Orlando, FL\\
2005 - 2007 	& Web Developer, cloudspace, Orlando, FL
\end{datetbl}\\[3px]

%------------------------------------------------------------------------------
\textbf{(c) PRODUCTS}\\[5pt]
\vspace{-1.5em}
\bibliographystyler{nsf}
\nociter{DK18a}
\nociter{HND*18}
\nociter{DKK20}
\nociter{KD13}
%\nociter{DK15c}
\nociter{BDD*21}
\bibliographyr{deblasio}

\bibliographystyleo{nsf}
\nociteo{DBZ12}
\nociteo{MDG*11}
\nociteo{MDPK19}
\nociteo{DGKM19}
\nociteo{DW16}
%\nociter{DK18d}
\bibliographyo{deblasio}
%------------------------------------------------------------------------------
\textbf{(d) SYNERGISTIC ACTIVITIES}\\[5pt]
\vspace{-1.5em}
\begin{enumerate}
\item \textbf{Conference service:} (i) Organizing committee for the NSF sponsored “Workshop on the Future of Algorithms in Biology (FAB)”, September 2018, Carnegie Mellon University, Pittsburgh, PA, (ii) Organizing committee for several Student Council Symposia 2014-2017, including in Africa and Latin America, (iii) Student Activities Co-Chair at the ACM-BCB October 2016, Seattle, WA,

\item \textbf{University service:} (i) Computer Science Representative to the Associate Graduate Council for the College of Science at the University of Arizona, 2012-13 academic year, (ii) Graduate Student Council, Computer Science Department, University of Arizona, 2010-2013, various posts incl. chair.

\item \textbf{Community service:} (i) Authored several papers related to building student lead computational biology groups and related issues, (ii) Member of the International Society for Computational Biology’s (ISCB) board of directors, 2016-2019, (iii) Member of the internal organization of the ISCB Student Council, various positions incl. executive team member and web committee chair.

\item \textbf{Mentoring:} (i) Mentor of an undergraduate student in the University of Pittsburgh’s Internship in Biomedical Research, Informatics and Computer Science (iBRIC) this work won best student paper at the 2019 ACM Conference on Bioinformatics, Computational Biology, and Health Informatics. (ii) Mentored a student though his masters thesis while a postdoc at Carnegie Mellon University. (iii) Currently mentoring one MS student and one BS student at the University of Texas at El Paso.

\item \textbf{Teaching:} (i) Instructor for an undergraduate/graduate class on computational biology algorithms at the University of Texas at El Paso. (ii) Co-instructor for a graduate emerging topics course at Carnegie Mellon University. (iii) Instructor for a graduate class at the University of Arizona that taught algorithmic concepts to new interdisciplinary graduate students.
\end{enumerate}


\end{document}
